---
title: "Ecobat Bat Activity Analysis"
author: '`r params$Author`'
date: '`r strftime(Sys.time(), format = "%d/%m/%Y")`'
output: word_document
params:
  n: NA
  Author: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE, comment=NULL)

#Libraries used
library(tidyverse) # Enables a consistent approach to data science
library(dplyr)
library(suncalc) # Suntimes
library(knitr)
library(lubridate)
library(ggplot2)
library(ggforce)
library(pander)

```




```{r}
# # for testing purposes - load in test data
# B_data <- read.csv("//smbhome.uscs.susx.ac.uk/brs28/Desktop/MammalSociety/Ecobat/Ecobat/WithinNight/Data/RiggedHill.csv")
#glimpse(B_data)

```


```{r}
#this is here for when the script is finalised and the Shiny app is deployed
#read data in from shiny
B_data <- params$n
```


```{r}

# Standardize Variables - make names consistent for further manipulation; can do the same for other bat sound analysis software e.g. Kaleidoscope. Make time zone local e.g `"Europe/London"`; adjusts for daylight saving automatically.


# if there is a separate column for date and time then join together to form a new column called Timestamp
if (("Date" %in% colnames(B_data) == TRUE) &
  ("Time" %in% colnames(B_data) == TRUE)) {

B_data$Timestamp <- paste(B_data$Date, B_data$Time) }

  
#Make Time Zone Local
B_data$DateTime <- lubridate::dmy_hms(B_data$Timestamp, tz = "Europe/London")

# change any instances of spec. to spp. in the species column
#B_data$Species <- stringr::str_replace(B_data$Species, "spec.", "spp." )


B_data$SppLoc <- paste(B_data$Species, B_data$Location.ID, sep = ' : ')

```


```{r}

# Create Useful Variables
# `Night` date at dusk
# `Month` month of observation `Jan, Feb, Mar....`
# `JustTime` time hh:mm of bat observation (12 hours added so plots correctly as `Night` i.e. dusk to dawn)
# `bat_time` time in seconds bat present see <https://rbats-blog.updog.co/2018/06/19/a-bat-time-metric/>


# if there is no information about the calls of the bats do this:

if ("Calls" %in% colnames(B_data) == FALSE)
   {

  B_data2 <- B_data %>% 
  mutate(Night = DateTime - lubridate::hours(12)) %>% # DateTime minus 12 hours
  mutate(Night = lubridate::as_date(Night)) %>%
  mutate(Month = lubridate::month(Night, label = T)) %>% # Make Month of observation
  mutate(JustTime = DateTime + lubridate::hours(12)) %>%
  mutate(JustTime = hms::as.hms(stringr::str_sub(as.character(JustTime), start = 12, end = 19))) %>%
  #mutate(Bat_time = (Calls * (Length + Distance)) / 1000) %>% 
  #Remove NA observations 
  filter(!is.na(Species)) %>%
  select(Night, JustTime, DateTime, Species, Month, Latitude, Longitude, Location.ID, SppLoc)
}

# if call info is provided, calculate 'Bat_time'

if ("Calls" %in% colnames(B_data) == TRUE)
   {
  B_data2 <- B_data %>% 
  mutate(Night = DateTime - lubridate::hours(12)) %>% # DateTime minus 12 hours
  mutate(Night = lubridate::as_date(Night)) %>%
  mutate(Month = lubridate::month(Night, label = T)) %>% # Make Month of observation
  mutate(JustTime = DateTime + lubridate::hours(12)) %>%
  mutate(JustTime = hms::as.hms(stringr::str_sub(as.character(JustTime), start = 12, end = 19))) %>%
  mutate(Bat_time = (Calls * (Length + Distance)) / 1000) %>% 
  #Remove NA observations 
  filter(!is.na(Species)) %>%
  select(Night, JustTime, DateTime, Species, Bat_time, Month, Latitude, Longitude, Location.ID, SppLoc)
}

     
# Change the format of the date from Y-m-d to d-m-Y:

# B_data2$Night2 <- as.Date(as.character(B_data2$Night, tz = "Europe/London", "%d/%m/%Y"), "%Y-%m-%d")
# 
# B_data2$Night2 <- format(as.Date(B_data2$Night, format = "%Y-%m-%d"), format = "%d/%m/%Y")
# 
# B_data2$Night3 <- as.Date(B_data2$Night2, format = "%d/%m/%Y")
# 
# glimpse(B_data2)
# 
# # B_data2$Night2 <- format(B_data2$Night, format=c("%d-%m-%Y"))
# # B_data2$Night2 <- as.Date(B_data2$Night, format=c("%d-%m-%Y"))


```


```{r}

# Create suntimes

# Use package `suncalcs` to make `sunset` and `sunrise` columns for each `Night` and the location (`Latitude` and `Longitude`) of the bat survey.

# Get number nights between first and last bat observation (plus 1 for dawn)
num_nights <- as.integer(difftime(max(B_data2$Night) , 
                                  min(B_data2$Night) , 
                                  units = c("days"))) + 1

# Make a date vector of nights between first and last bat observation.
nightlist <- seq.Date(from=min(B_data2$Night), 
                   length.out = num_nights +1, 
                   by='days')

# Get suntimes for date vector and Location (Latitude and Longitude)
setdata <- getSunlightTimes(date = nightlist, 
                            lat = median(B_data2$Latitude, na.rm = T), 
                            lon = median(B_data2$Longitude, na.rm = T), 
                            tz = "Europe/London")

# Duplicate data.frame to make sunrise data
risedata <- setdata

# Select  sunset date and time
setdata <- setdata %>% 
  select(date, sunset) %>% 
  mutate(date = lubridate::as_date(date))

# Select  sunrise date and time
risedata <- risedata %>% 
  select(date, sunrise) %>% 
  mutate(date = lubridate::as_date(date)) %>%
  mutate(date = date - lubridate::days(1))


# Combine sunset and risedata by 
sun_data <- dplyr::full_join(setdata, risedata, by="date")

# Rename date as Night
colnames(sun_data) <- c("Night", "sunset", "sunrise")

sun_data <- sun_data %>% 
  mutate(night_length_hr = as.numeric(difftime(sunrise, sunset, units='hours')),
         night_length_min = as.numeric(difftime(sunrise, sunset, units='mins')))


# Join bat data with the sundata by Night
joined_data <- dplyr::left_join(B_data2, sun_data, by="Night")

```


```{r}
#  ## Create Variables Relative to Suntimes and Bat Observation 
# 
#  Variables relative to suntimes and bat observation   
# 
# * `post_set_min` bat observation time minutes after sunset  
#  * `pre_rise_min` bat observation time minutes before sunrise   
#  * `post_set_hr` bat observation time hours after sunset  
#  * `pre_rise_hr` bat observation time hours before sunrise   
#  * `post_set_hr_int` bat observation time as an integer (hour) after sunset  
#      + `-0.5` to `0.49` hours is `0` hour   
#      + `0.5` to `1.49` hours is `1` hour   
#      + `1.5` to `2.49` hours is `2` hour   
#      + `2.5` to `3.49` hours is `3` hour ect...  

#  * `pre_rise_hr_int` bat observation time as an integer (hour) before sunrise  
#      + `-0.5` to `0.49` hours is `0` hour   
#      + `0.5` to `1.49` hours is `1` hour   
#      + `1.5` to `2.49` hours is `2` hour   
#      + `2.5` to `3.49` hours is `3` hour ect...   
#  * `night_length_hr`  length of the night in hours    


# To make sure difference is in minutes/hours etc... use difftime 
All_data <- joined_data %>% 
  mutate(post_set_min = as.numeric(difftime(DateTime, sunset, units='mins')),
         pre_rise_min = as.numeric(difftime(sunrise, DateTime, units='mins')),
         post_set_hr = as.numeric(difftime(DateTime, sunset, units='hours')),
         pre_rise_hr = as.numeric(difftime(sunrise, DateTime, units='hours')),
         post_set_hr_int = as.integer(round(post_set_hr, digits = 0)),
         pre_rise_hr_int = as.integer(round(pre_rise_hr, digits = 0)))

```


## Roost Emergence Time and Bat Observation

Based on: _Russ, Jon. 2012. British Bat Calls a Guide to Species Identification._ 
_Pelagic Publishing._

For more information see <https://rbats-blog.updog.co/2018/05/29/bat-emergence/>

```{r}
#Russ(2012) Bat roost emergence times minutes after sunset
Species <- c("Barbastella barbastellus",
                "Eptesicus serotinus",
                "Myotis alcathoe",
                "Myotis bechsteinii",
                "Myotis brandtii",
                "Myotis daubentonii",
                "Myotis mystacinus",
                "Myotis nattereri",
                "Myotis spp.",
                "Nyctalus leisleri",
                "Nyctalus noctula",
                "Nyctalus spp.",
                "Pipistrellus nathusii",
                "Pipistrellus pipistrellus",
                "Pipistrellus pygmaeus",
                "Pipistrellus spp.",
                "Plecotus auritus",
                "Plecotus austriacus",
                "Rhinolophus ferrumequinum",
                "Rhinolophus hipposideros")

lower <- c(25, 20, 30, 30, 30, 50, 30, 35, 30, 8, 5, 5, 18, 22, 22, 18, 40, 40, 35, 35)
upper <- c(60, 25, 35, 33, 35, 70, 35, 55, 70, 18, 9, 18, 28, 32, 28, 32, 60, 60, 48, 50)
russ <- tibble(Species, lower, upper)

```


```{r}
#Join with Jon Russ data with bat observation data All_data
All_data <- dplyr::left_join(All_data, russ, by = "Species")

```

# Summary Tables  

## Sun Times

```{r}
Table <- All_data %>% 
  select(Night, sunset, sunrise) %>% 
  distinct() %>% 
  mutate(night_length = round(as.numeric(difftime(sunrise, sunset, units='hours')), digits = 1),
         sunset = stringr::str_sub(as.character(sunset), 11, 16),
         sunrise = stringr::str_sub(as.character(sunrise), 11, 16))

colnames(Table) <- c("Night (y-m-d)", "Sunset (hh:mm)", "Sunrise (hh:mm)", "Night Length (hours)")


knitr::kable(Table, align = ("lrrr"))

```

\pagebreak

## Count All Bat Passes

```{r}

# Aggregate data into Species and count
Table <- All_data %>%
  group_by(Species) %>% 
  count() %>% 
  arrange(desc(n))


#Change column Names so more meaningful  
colnames(Table) <- c("Species Name", "Count (No)")

# kable is a simple table generator
knitr::kable(Table)

```


\pagebreak

## Bat Passes by Night

The number of passes per survey night by each species

```{r}
Table <- All_data %>%
  group_by(Species, Night) %>% 
  count() %>% 
  spread(Night, n)

# Make all NA's = 0
Table[is.na(Table)] <- 0

new <- melt(Table, id="Species")
new2 <- melt(new, id=c("Species", "variable"))

new3 <- t(Table)
results='asis' #important to run this as it ensures the raw table output isn't processed further by knitr

panderOptions('table.split.table', 80)
pander(Table, style="rmarkdown")


```


\pagebreak

## Bat Passes per Hour by Night

This calculates the average bat passes per night by dividing the total number of
bat passess for the night by the the night length (hrs) (`sunrise` - `sunset`).

```{r}
Table <- All_data %>%
  group_by(Species, Night, night_length_hr) %>% 
  # count number of passes per night by species - makes coloumn "n""
  count() %>% 
  # calculate average bat passes per hour for each Night and species
  summarise(Act_per_hr = n / night_length_hr) %>%
  # Remove Night Length column from the Table
  select(-night_length_hr) %>% 
  spread(Night, Act_per_hr)

# Make all NA's = 0
Table[is.na(Table)] <- 0

# simple table with 1 decimal point
knitr::kable(Table, digits = 1)

```

\pagebreak

## Bat Passes by Month

```{r}
Table <- All_data %>%
  group_by(Species, Month) %>% 
  count() %>% 
  spread(Month, n)

# Make all NA's = 0
Table[is.na(Table)] <- 0

# simple table
knitr::kable(Table)

```
\pagebreak

`r if("Bat_time" %in% colnames(All_data) == TRUE) {'## Time (Seconds) Bat Present' }`


```{r}

if("Bat_time" %in% colnames(All_data) == TRUE) {

Table <- All_data %>%
  group_by(Night, Species) %>%
  summarise(total_act = sum(Bat_time)) %>%
  spread(Night, total_act)

# Make all NA's = ""
Table[is.na(Table)] <- 0

# simple table with 1 decimal point
knitr::kable(Table, digits = 1)

}

```

\pagebreak

`r if("Bat_time" %in% colnames(All_data) == TRUE) {'## Time (Minutes and Seconds) Bat Present' }`


```{r}

if("Bat_time" %in% colnames(All_data) == TRUE) {
  
Table <- All_data %>%
  group_by(Night, Species) %>%
  summarise(total_act = sum(Bat_time)) %>%
  ungroup(Night, Species) %>%
  mutate(total_act = round(total_act, digits = 0),
         total_act = as.character(lubridate::seconds_to_period(total_act))) %>%
  spread(Night, total_act)

# Make all NA's = ""
Table[is.na(Table)] <- ""

# simple table
knitr::kable(Table)
}


```

\pagebreak

## Bat Passes by Hour after Sunset

```{r}
Table <- All_data %>%
  group_by(Species, post_set_hr_int) %>% 
  count() %>% 
  spread(post_set_hr_int, n)

# Make all NA's = 0
Table[is.na(Table)] <- 0

# simple table
knitr::kable(Table)

```
\pagebreak

## Bat Passes _Near_ a Roost by Night (Russ 2012)

```{r}
Table <- All_data %>% 
  filter(post_set_min <= upper) %>% 
  group_by(Night, Species) %>% 
  count() %>% 
  spread(Night, n)

# Make all NA's = 0
Table[is.na(Table)] <- 0

# simple table
knitr::kable(Table)
```


\pagebreak
```{r fig.width=10, fig.height=12}

# plot out each pass 

SpeciesLoc <- unique(All_data$SppLoc)


#for(i in seq_along(SpeciesLoc)) {
  
npage <- ceiling(length(SpeciesLoc)/6)
  
for(i in seq_len(npage)) {

print(All_data %>%
  ggplot(aes(Night, post_set_min)) +
  geom_point(size=4, alpha = 0.5, position =
               position_jitter(w = 1, h = 0)) +
  geom_line(data = sun_data, aes(Night, night_length_min),
            linetype = "dashed", colour = "red") +
  xlab("\nMonth") + 
  ylab("Minutes after sunset\n") +
  theme_bw() +
  theme (legend.position = "none") +
  theme (axis.title.y = element_text(colour="black", size=18,
                                     face="bold")) +
  theme (axis.title.x = element_text(colour="black", size=18,
                                     face="bold")) +
  theme(strip.text.x = element_text(size=18, face="bold")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black",
                               linetype="solid")) +
  theme(axis.text.x = element_text(size=16, hjust=0.5, vjust=1,
                                   colour = "black")) +
  theme(axis.text.y = element_text(size = 16, colour = "black")) +
  facet_wrap_paginate(SppLoc~., ncol=2, nrow=3, scales="fixed", page=i)) 
 
}



```




\pagebreak 
```{r fig.width=22, fig.height=16}

# create a list of all of the different species
spp_list <- unique(All_data$Species)


xLab <- "\nTime after sunset (mins)"
Caption <- "\nFirst 90 minutes after sunset. \nGrey bars are emergence times adapted from (Russ 2012)"


for (i in seq_len(length(unique(All_data$Location.ID)))) {
  
print(ggplot(All_data, aes(x=post_set_min, y=Species, colour=Species)) +
    geom_segment(aes(x=lower, xend=upper, y=Species, yend=Species),
                 size = 25, colour="grey") +
  geom_point(size=5, alpha=0.7,  position = position_jitter(height = 0.3)) +
  labs(x = xLab, caption = Caption) +
  scale_x_continuous(breaks=c(-15, 0, 15, 30, 45, 60, 75, 90),
                     limits = c(-15, 90)) +
  geom_hline(yintercept = c(seq_len(length(spp_list)-1) + 0.5),
             colour = "black", linetype = "dotted") +
  scale_y_discrete(drop=FALSE) +
  theme_bw() +
  theme(legend.position = "none") +
  theme(plot.caption = element_text(colour = "black", size = 30)) +
  theme(strip.text.x = element_text(size=30, face="bold")) +
  theme(axis.title.y = element_blank()) +
  theme(axis.title.x = element_text(colour = "black", size = 30,
                                     face = "bold")) +
  theme(axis.text.x = element_text(size = 24, hjust=0.5, vjust=1,
                                   colour = "black",
                                   face = "bold")) +
  theme(axis.text.y = element_text(size = 24, colour = "black",
                                   face = "bold.italic")) +
  theme(panel.background = element_rect(fill = "white")) +
  theme(panel.grid.major.x = element_line(colour = "black",
                                          linetype = "dotted"), 
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(), 
        panel.grid.minor.y = element_blank()) +
  theme (axis.ticks = element_blank()) +
  facet_wrap_paginate(~Location.ID, ncol=1, nrow=1, page=i))
}


```
























