---
title: "Ecobat Bat Activity Analysis"
author: '`r params$Author`'
date: '`r strftime(Sys.time(), format = "%d/%m/%Y")`'
output: word_document
params:
  n: NA
  Author: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE, comment=NULL)
#load packages
library(rmarkdown)
library(ggplot2)
library(knitr)
library(pander)
library(plyr)
library(rcompanion)
library(tidyr)
library(lubridate)
```


```{r}
#insert file path file
#this is here so I can test the script before it's linked with the Shiny app
#df <- read.csv("C:/Users/Sophie/Documents/Bats/Fake Data/paper2.csv", header = TRUE)
#dfa <- read.csv("C:/Users/Sophie/Downloads/download (6).csv", header = TRUE)
#df <- read.csv("C:/Users/Sophie/Downloads/download (8).csv", header = TRUE)
```

```{r}
#this is here for when the script is finalised and the Shiny app is deployed
#read data in from shiny
df <- params$n
```

```{r}
#date<-as.Date(df$date) #for date graphs later, convert date column into date objects
#date<-format(date, format="%d/%m/%Y") #formats dates
date<-as.Date(df$date) #for date graphs later, convert date column into date objects
date<-parse_date_time(df$date,"ymd")
if(is.na(date)) {date<-parse_date_time(df$date,"dmy")}
nights<-length(unique(df$date)) #calculate number of nights recorded for
species<-length(unique(df$species)) #calculate number of species recorded
ldetector<-unique(df$detector_make) #pull the names of the detectors used
llocation<-unique(df$location_name) #pull the locations recorded at
lspecies<-unique(df$species) #list what species were recorded - potentially for graph legends later
cbbPalette <- c("#D55E00", "#0072B2","#56B4E9","#009E73","#E69F00") #set colour palette for graphs
greys <- c("#FFFFFF", "#999999", "#909090", "#888888", "#838383",  "#777777", "#747474", "#666666", "#656565") #set colour palette for boxplot fills
spl<-nlevels(df$species) #counts the number of species recorded. this actually does same as 'species'
df$location_name <- factor(df$location_name)

```

###Summary
Bat surveys were conducted at `r (llocation)`, for `r (nights)` nights between `r min(date)` and `r max(date)`, using `r ldetector` static bat detectors. The maximum of passes recorded in a single night was `r max(df$passes)` passes, and `r species` species were recorded.

The reference range dataset was stratified to include:

`r if('1' %in% df$date_filter) {'* Only records from within 30 days of the survey date.  '}`

`r if('0' %in% df$date_filter) {'* Records from any time of year.  '}`

`r if('200' %in% df$location_filter) {'* Only records from within 200km^2^ of the survey location.  '}`

`r if('100' %in% df$location_filter) {'* Only records from within 100km^2^ of the survey location.  '}`

`r if("NO" %in% df$location_filter) {'* Records from across the entire UK.  '}`

`r if("No" %in% df$detector_make_filter) {'* Records using any make of bat detector.  '}`

`r if("Batbox" %in% df$detector_make_filter) {'* Only records using Batbox bat detectors.  '}`

`r if("Ciel" %in% df$detector_make_filter) {'* Only records using Ciel bat detectors.  '}`

`r if("Courtpan" %in% df$detector_make_filter) {'* Only records using Courtpan bat detectors.  '}`

`r if("Elekon" %in% df$detector_make_filter) {'* Only records using Elekon bat detectors.  '}`

`r if("Magenta" %in% df$detector_make_filter) {'* Only records using Magenta bat detectors.  '}`

`r if("Peersonic" %in% df$detector_make_filter) {'* Only records using Peersonic bat detectors.  '}`

`r if("Pettersson" %in% df$detector_make_filter) {'* Only records using Pettersson bat detectors.  '}`

`r if("Titley Scientific" %in% df$detector_make_filter) {'* Only records using Titley Scientific bat detectors.  '}`

`r if("Wildlife Acoustics" %in% df$detector_make_filter) {'* Only records using Wildlife Acoustics bat detectors.  '}`

***

```{r}
recordsum <- ddply(df, c("sref", "species"), summarise, #summarise to produce a measure of how many records each species has at each location to make graphs better
                   surv = length(species))
#now merge this back into the original csv - we don't want to delete any files at this stage
wp<- merge(df, recordsum, c("sref","species")) #merge with original dataset - adds surv column onto end of dataset
ys<-subset(wp, surv >= 5) #subset to only include species with more than 5 records per location

spn<-length(unique(ys$species)) #calculate how many species had more than 5 records per location
loc<-length(unique(ys$sref)) #calculate how many locations the new subsetted dataframe
lspecies<-(unique(ys$species)) #pull names of species from new subsetted dataframe
date2<-as.Date(ys$date,format="%d/%m/%Y") #for date graphs later, convert date column into date objects
if(is.na(date2)) {ys$date<-as.Date(ys$date)}
ys$date<-parse_date_time(ys$date,"ymd")
if(is.na(ys$date)) {ys$date<-parse_date_time(ys$date,"dmy")}
date2<-parse_date_time(date2, "ymd")
if(is.na(ys$date)) {ys$date<-date2}
ys$date<-as.Date(ys$date)
```


####Table 1
Summary table showing the number of nights recorded bat activity fell into each activity band for each species.
```{r}
library(plyr)
actdata <- ddply(df, c("location_name", "species"), summarise,
                 Nights.high = sum(activity_level=="high"),
                 Nights.modhigh = sum(activity_level=="medium/high"),
                 Nights.mod = sum(activity_level=="medium"),
                 Nights.lowmod = sum(activity_level=="low/medium"),
                 Nights.low = sum(activity_level=="low"))

#rename columns
names(actdata)[names(actdata)=="location_name"] <- "Location"
names(actdata)[names(actdata)=="species"] <- "Species/Species Group"
names(actdata)[names(actdata)=="Nights.high"] <- "Nights of High Activity"
names(actdata)[names(actdata)=="Nights.modhigh"] <- "Nights of Moderate/ High Activity"
names(actdata)[names(actdata)=="Nights.mod"] <- "Nights of Moderate Activity"
names(actdata)[names(actdata)=="Nights.lowmod"] <- "Nights of Low/ Moderate Activity"
names(actdata)[names(actdata)=="Nights.low"] <- "Nights of Low Activity"                  

library(knitr)
results='asis'#important to run this as it ensures the raw table output isn't processed further by knitr
datatable2<-actdata
emphasize.italics.cols(2) #second column needs to be in italics i.e. species names
panderOptions("table.split.table", Inf) #don't split table
pander(datatable2, style = 'rmarkdown', keep.line.breaks=TRUE)
```

***

####Table 2
Summary table showing key metrics for each species recorded.
```{r}
library(plyr)
library(rcompanion)

con<-subset(wp, surv>2) #subset dataset to only include records with more than one night of surveying
confint<-groupwiseMedian(percentile ~ sref + species, #code to get confidence intervals
                          data       = con, 
                          conf       = 0.95, 
                          R          = 1000,
                          percentile = TRUE, 
                          bca        = FALSE, 
                          digits     = 3)

mm<-merge(con, confint) #merge with subsetted dataset to put columns with the confidence intervals on the end
mm$confint = paste(mm$Percentile.lower, mm$Percentile.upper, sep=" - ") #add a new column with CIs merged

non<-subset(wp,surv=="1") #subset dataset to only include records with one night of surveying
if(nrow(non)>0) {
  non$n <- 0 #add empty columns to enable merger
non$Median <- 0
non$Conf.level <- 0
non$Percentile.upper <- 0
non$Percentile.lower <- 0
non$confint <- 0}

please<-rbind(mm, non) #join the two datasets back together

library(plyr) #ddply as normal
mdata2 <- ddply(please, c("location_name", "species"), summarise,
               Median.percentile = ceiling(median(percentile)),#finds median percentile
               conf = max(confint),
               Highest.perc = max(percentile), #returns max percentiles
               Number.nights = length(date), #returns how many nights of data in the dataset
               Reference.range.size = mean(reference_range_size)) #returns reference range size - i used mean as it should be the 
#same in each row because same species same location
names(mdata2)[names(mdata2)=="location_name"] <- "Location"
names(mdata2)[names(mdata2)=="species"] <- "Species/Species Group"
names(mdata2)[names(mdata2)=="Median.percentile"] <- "Median Percentile"
names(mdata2)[names(mdata2)=="conf"] <- "95% CIs"
names(mdata2)[names(mdata2)=="Highest.perc"] <- "Max Percentile"
names(mdata2)[names(mdata2)=="Number.nights"] <- "Nights Recorded"
names(mdata2)[names(mdata2)=="Reference.range.size"] <- "Reference Range"

library(knitr)
library(pander)
results='asis' #important to run this as it ensures the raw table output isn't processed further by knitr
medtable2<-mdata2
emphasize.italics.cols(2)
panderOptions("table.split.table", Inf)
panderOptions("table.split.cells", Inf)
pander(medtable2, style = 'multiline', keep.line.breaks=TRUE,justify = c('right', 'left', 'centre', 'centre', 'centre', 'centre', 'centre'))

```

***

```{r}
#not sure why this is here again
#as it's identical to code above
#recordsum <- ddply(df, c("Location", "Species"), summarise,
#                   surv = length(Species))
#now merge this back into the original csv - we don't want to delete
#any files at this stage
#wp<- merge(df, recordsum, c("Location","Species")) #merge with original dataset - adds surv column onto end of dataset
#ys<-subset(wp, surv >= 5) #subset to only include species with more than 5 records per location

#spn<-length(unique(ys$Species))
#loc<-length(unique(ys$Location))
#lspecies<-(unique(ys$Species))
```





###Figures
```{r fig.width=9, fig.height=6}

#boxplot if 1 location
loc<-nlevels(ys$sref)

if(loc=="1") {graphbox<-ggplot(ys, aes(x=species, y=percentile))+ #add lines first
  geom_hline(aes(yintercept=0), linetype="dashed", color="#000000") +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  geom_boxplot(df, mapping = aes(fill=species))+
  xlab("Species")+
  ylab("Bat Activity Level (Percentile)")+
  scale_fill_manual(values=greys)+
  scale_y_continuous(breaks=seq(0,100,20)) +
  expand_limits(y=c(0,100))+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(linetype="blank"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90, face="italic", size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18),
        legend.position="none")
graphbox}

#endcode for boxplot
```

`r if(loc=="1") {'**Figure 1.**\n The recorded activity of bats during the survey. The centre line indicates the median activity level whereas the box represents the interquartile range (the spread of the middle 50% of nights of activity)  '}`

```{r fig.width=9, fig.height=6}

#boxplot if 2-5 location but only one species
loc<-nlevels(ys$sref)

if(loc>2 & loc<5 & spn=="1") {graphboxb<-ggplot(ys, aes(x=location_name, y=percentile))+ #add lines first
  geom_hline(aes(yintercept=0), linetype="dashed", color="#000000") +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  geom_boxplot(ys, mapping = aes(fill=location_name))+
  xlab("Location name")+
  ylab("Bat Activity Level (Percentile)")+
  scale_fill_manual(values=greys)+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) +
  expand_limits(y=c(0,100))+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(linetype="blank"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18),
        legend.position="none")
graphboxb}

#endcode for boxplot
```

`r if(loc>2 & loc<5 & spn=="1") {'**Figure 1.**\n Differences in activity of bats between static detector locations. The centre line indicates the median activity level whereas the box represents the interquartile range (the spread of the middle 50% of nights of activity)  '}`

```{r fig.width=9, fig.height=6}

#boxplot if 2-5 location and more one species
loc<-nlevels(ys$sref)

if(loc>2 & loc<5 & spn>1) {graphboxb<-ggplot(ys, aes(x=location_name, y=percentile))+ #add lines first
  geom_hline(aes(yintercept=0), linetype="dashed", color="#000000") +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  geom_boxplot(ys, mapping = aes(fill=location_name))+
  xlab("Location name")+
  ylab("Bat Activity Level (Percentile)")+
  scale_fill_manual(values=greys)+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) +
  expand_limits(y=c(0,100))+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(linetype="blank"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18),
        legend.position="none")+
  facet_grid(. ~ species) +
    theme(strip.text.x = element_text(size=16, face="italic"))
graphboxb}

#endcode for boxplot
```

`r if(loc>1 & spn>"1") {'**Figure 1.**\n Differences in bat activity between static detector locations. The centre line indicates the median activity level whereas the box represents the interquartile range (the spread of the middle 50% of nights of activity)  '}`

```{r fig.width=9, fig.height=8}

#boxplot if more than 5 location and one species
loc<-nlevels(ys$sref)

if(loc>=5 & spn=="1") {graphboxc<-ggplot(ys, aes(x=location_name, y=percentile))+ #add lines first
  geom_hline(aes(yintercept=0), linetype="dashed", color="#000000") +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  geom_boxplot(ys, mapping = aes(fill=location_name))+
  xlab("Location name")+
  ylab("Bat Activity Level (Percentile)")+
  scale_fill_manual(values=greys)+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) +
  expand_limits(y=c(0,100))+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18),
        legend.position="none")+
  facet_wrap( ~ species, ncol=3) +
    theme(strip.text.x = element_text(size=16, face="italic"))
graphboxbc}

#endcode for boxplot
```

`r if(loc>=5 & spn=="1") {'**Figure 1.**\n Differences in activity between static detector locations, split by species and location. The centre line indicates the median activity level whereas the box represents the interquartile range (the spread of the middle 50% of nights of activity)  '}`

```{r fig.width=9, fig.height=8}

#boxplot if more than 2 location and more than one species
loc<-nlevels(ys$sref)

if(loc>=5 & spn>"1") {graphboxc<-ggplot(ys, aes(x=location_name, y=percentile))+ #add lines first
  geom_hline(aes(yintercept=0), linetype="dashed", color="#000000") +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  geom_boxplot(ys, mapping = aes(fill=location_name))+
  xlab("Location name")+
  ylab("Bat Activity Level (Percentile)")+
  scale_fill_manual(values=greys)+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) +
  expand_limits(y=c(0,100))+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18),
        legend.position="none")+
  facet_wrap( ~ species, ncol=3) +
    theme(strip.text.x = element_text(size=16, face="italic"))
graphboxc}

#endcode for boxplot
```

`r if(loc>=5 & spn>"1") {'**Figure 1.**\n Differences in activity between static detector locations, split by species and location. The centre line indicates the median activity level whereas the box represents the interquartile range (the spread of the middle 50% of nights of activity)  '}`


```{r fig.width=9, fig.height=8}
## date ~ percentile graph if 1 location, 1 species
#if less than 21 days
ys$date<-as.Date(ys$date)
ys$date2<-format(ys$date, "%d/%m/%Y")

if((difftime(max(ys$date),min(ys$date), units='days')<=21) & loc=="1" & spn=="1"){ graphD<-ggplot(ys, aes(x= date, y= percentile)) +
  geom_point(ys, size=3, 
             mapping = aes(x=date, y= percentile, color=activity_level, shape=1))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","d"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "3 days", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(linetype="blank"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  graphD}

##end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')<=21) & loc=="1" & spn=="1") {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey.  '}`

```{r fig.width=9, fig.height=8}
## date ~ percentile graph if 1 location, >1 species
#if less than 21 days

if((difftime(max(ys$date),min(ys$date), units='days')<=21) & loc=="1" & spn>1) {graphD<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1, 
             mapping = aes(x=date, y= percentile, color=activity_levels))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) +
  scale_x_date(name = "Date", date_breaks = "3 days", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(species ~ .) +
  theme(strip.text.y = element_text(size=16, face="italic"))
graphD}

##end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')<=21) & loc=="1" & spn>1) {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by species.  '}`

```{r fig.width=9, fig.height=8}
## date ~ percentile graph if 2-5 locations + >1 species
#less than 21 days 

if((difftime(max(ys$date),min(ys$date), units='days')<=21) & loc>1 & loc<5 & spn>1) {graphE<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1,
             mapping = aes(x=ys$date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "1 week", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(species ~ location_name) +
  theme(strip.text.y = element_text(size=16, face="italic"),
        strip.text.x = element_text(size=16))
graphE}

#end code for date graph
```
`r if((difftime(max(ys$date),min(ys$date), units='days')<=21) & loc>1 & loc<5 & spn>1) {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location and species.  '}`

```{r fig.width=9, fig.height=10}
# date ~ percentile graph if 1 species and 2-5 locations
#less than 21 days 

if((difftime(max(ys$date),min(ys$date), units='days')<=21) & loc>1 & loc<5 & spn=="1") {graphE<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1, 
             mapping = aes(x=date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "1 week", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18))+
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(. ~ location_name) +
  theme(strip.text.x = element_text(size=16))
graphE}

#end code for date graph
```
`r if((difftime(max(ys$date),min(ys$date), units='days')<=21) & loc>1 & loc<5 & spn=="1") {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location.  '}`

```{r fig.width=9, fig.height=10}
## date ~ percentile graph if >5 location + >1 species
#less than 21 days

if((difftime(max(ys$date),min(ys$date), units='days')<=21) & loc>=5 & spn>1) {graphF<-ggplot(ys, aes(x= ys$date, y= percentile))+
  geom_point(ys, size=3, shape=1,
             mapping = aes(x=ys$date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "1 week", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_wrap(species ~ location_name, ncol=2) +
  theme(strip.text.y = element_text(size=16, face="italic"),
        strip.text.x = element_text(size=16))
graphF}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')<=21) & loc>=5 & spn>1) {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location and species.  '}`


```{r fig.width=9, fig.height=12}
# date ~ percentile graph if 1 species and >5 location
#less than 21 days

if((difftime(max(ys$date),min(ys$date), units='days')<=21) & loc>=5 & spn=="1"){ graphF<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1, 
             mapping = aes(x=date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "1 week", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18))+
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_wrap( ~ location_name, ncol=2) +
  theme(strip.text.x = element_text(size=16))
graphF}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')<=21) & loc>=5 & spn=="1") {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location.  '}`

```{r fig.width=9, fig.height=8}
## date ~ percentile graph if 1 location, 1 species
#if time difference is between 21 and 50 days 

if((difftime(max(ys$date),min(ys$date), units='days')>21) & (difftime(max(ys$date),min(ys$date), units='days')<50) & loc=="1" & spn=="1"){ graphG<-ggplot(ys, aes(x= date, y= percentile)) +
  geom_point(ys, size=3, 
             mapping = aes(x=date, y= percentile, color=activity_level, shape=1))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "1 week", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(linetype="blank"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  graphG}

##end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>21) & (difftime(max(ys$date),min(ys$date), units='days')<50) & loc=="1" & spn=="1") {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey.  '}`

```{r fig.width=9, fig.height=8}
## date ~ percentile graph if 1 location, >1 species
#if time difference is between 21 and 50 days 

if((difftime(max(ys$date),min(ys$date), units='days')>21) & (difftime(max(ys$date),min(ys$date), units='days')<50) & loc=="1" & spn>1) { graphG<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1,
             mapping = aes(x=date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) +
  scale_x_date(name = "Date", date_breaks = "1 week", date_labels = "%d %b %y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(species ~ .) +
  theme(strip.text.y = element_text(size=16, face="italic"))
graphG}

##end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>21) & (difftime(max(ys$date),min(ys$date), units='days')<50) & loc=="1" & spn>1) {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by species.  '}`

```{r fig.width=10, fig.height=10}
## date ~ percentile graph if 2-5 locations + >1 species
#if time difference is between 21 and 50 days 

if((difftime(max(ys$date),min(ys$date), units='days')>21) & (difftime(max(ys$date),min(ys$date), units='days')<50) & loc>1 & loc<5 & spn>1){ graphh<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1,
             mapping = aes(x=ys$date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "1 week", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(species ~ location_name) +
  theme(strip.text.y = element_text(size=10, face="italic"),
        strip.text.x = element_text(size=16))
graphh}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>21) & (difftime(max(ys$date),min(ys$date), units='days')<50) & loc>1 & loc<5 & spn>1) {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location and species.  '}`


```{r fig.width=9, fig.height=10}
# date ~ percentile graph if 1 species and 2-5 locations
#if time difference is between 21 and 50 days 

if((difftime(max(ys$date),min(ys$date), units='days')>21) & (difftime(max(ys$date),min(ys$date), units='days')<50) & loc>1 & loc<5 & spn=="1"){ graphh<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1, 
             mapping = aes(x=date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "1 week", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18))+
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(. ~ location_name) +
  theme(strip.text.x = element_text(size=16))
graphh}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>21) & (difftime(max(ys$date),min(ys$date), units='days')<50) & loc>1 & loc<5 & spn=="1") {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location.  '}`

```{r fig.width=9, fig.height=10}
## date ~ percentile graph if >5 location + >1 species
#if time difference is between 21 and 50 days 

if((difftime(max(ys$date),min(ys$date), units='days')>21) & (difftime(max(ys$date),min(ys$date), units='days')<50) & loc>=5 & spn>1) {graphi<-ggplot(ys, aes(x= ys$date, y= percentile))+
  geom_point(ys, size=3, shape=1,
             mapping = aes(x=ys$date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "1 week", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_wrap(species ~ location_name, ncol=2) +
  theme(strip.text.y = element_text(size=16, face="italic"),
        strip.text.x = element_text(size=16))
graphi}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>21) & (difftime(max(ys$date),min(ys$date), units='days')<50) & loc>=5 & spn>1) {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location and species.  '}`


```{r fig.width=9, fig.height=12}
# date ~ percentile graph if 1 species and >5 location
#if time difference is between 21 and 50 days 

if((difftime(max(ys$date),min(ys$date), units='days')>21) & (difftime(max(ys$date),min(ys$date), units='days') <50) & loc>=5 & spn=="1"){ graphi<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1, 
             mapping = aes(x=date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "1 week", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18))+
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_wrap( ~ location_name, ncol=2) +
  theme(strip.text.x = element_text(size=16))
graphi}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>21) & (difftime(max(ys$date),min(ys$date), units='days') <50) & loc>=5 & spn=="1") {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location.  '}`

```{r fig.width=9, fig.height=8}
## date ~ percentile graph if 1 location, 1 species
#if time diff between 50 and 300 days

if((difftime(max(ys$date),min(ys$date), units='days')>50) & (difftime(max(ys$date),min(ys$date), units='days')<300) & loc=="1" & spn=="1"){ graphj<-ggplot(ys, aes(x= date, y= percentile)) +
  geom_point(ys, size=3, 
             mapping = aes(x=date, y= percentile, color=activity_level, shape=1))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "3 weeks", date_labels = "%d %b %y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(linetype="blank"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
graphj}

##end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>50) & (difftime(max(ys$date),min(ys$date), units='days') <300) & loc=="1" & spn=="1") {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey.  '}`

```{r fig.width=9, fig.height=10}
## date ~ percentile graph if 1 location, >1 species
#if time diff between 50 and 300 days

if((difftime(max(ys$date),min(ys$date), units='days')>50) & (difftime(max(ys$date),min(ys$date), units='days')<300) & loc=="1" & spn>1) { graphj<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, 
             mapping = aes(x=date, y= percentile, color=activity_level, shape=1))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) +
  scale_x_date(name = "Date", date_breaks = "3 weeks", date_labels = "%d %b %y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(species ~ .) +
  theme(strip.text.y = element_text(size=16, face="italic"))
graphj}

##end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>50) & (difftime(max(ys$date),min(ys$date), units='days') <300) & loc=="1" & spn>1) {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by species.  '}`

```{r fig.width=9, fig.height=10}
## date ~ percentile graph if 2-5 locations + >1 species
#if time diff between 50 and 300 days

if((difftime(max(ys$date),min(ys$date), units='days')>50) & (difftime(max(ys$date),min(ys$date), units='days')<300) & loc>1 & loc<5 & spn>1) {graphk<-ggplot(ys, aes(x= ys$date, y= percentile))+
  geom_point(ys, size=3, shape=1,
             mapping = aes(x=ys$date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "3 weeks", date_labels = "%d %b %y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(species ~ location_name) +
  theme(strip.text.y = element_text(size=16, face="italic"),
        strip.text.x = element_text(size=16))
graphk}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>50) & (difftime(max(ys$date),min(ys$date), units='days') <300) & loc>1 & loc<5 & spn>1) {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location and species.  '}`


```{r fig.width=9, fig.height=10}
# date ~ percentile graph if 1 species and 2-5 locations
#if time diff between 50 and 300 days

if((difftime(max(ys$date),min(ys$date), units='days')>50) & (difftime(max(ys$date),min(ys$date), units='days')<300) & loc>1 & loc<5 & spn=="1"){ graphk<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1, 
             mapping = aes(x=date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "3 weeks", date_labels = "%d %b %y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18))+
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(. ~ location_name) +
  theme(strip.text.x = element_text(size=16))
graphk}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>50) & (difftime(max(ys$date),min(ys$date), units='days') <300) & loc>1 & loc<5 & spn=="1") {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location.  '}`

```{r fig.width=9, fig.height=12}
## date ~ percentile graph if >5 location + >1 species
#if time diff between 50 and 300 days

if((difftime(max(ys$date),min(ys$date), units='days')>50) & (difftime(max(ys$date),min(ys$date), units='days') <300) & loc>=5 & spn>1) {graphl<-ggplot(ys, aes(x= ys$date, y= percentile))+
  geom_point(ys, size=3, shape=1,
             mapping = aes(x=ys$date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "3 weeks", date_labels = "%d %b %y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_wrap(species ~ location_name, ncol=2) +
  theme(strip.text.y = element_text(size=16, face="italic"),
        strip.text.x = element_text(size=16))
graphl}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>50) & (difftime(max(ys$date),min(ys$date), units='days') <300) & loc>=5 & spn>1) {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location and species.  '}`


```{r fig.width=9, fig.height=12}
# date ~ percentile graph if 1 species and >5 location
#if time diff between 50 and 300 days

if((difftime(max(ys$date),min(ys$date), units='days')>50) & (difftime(max(ys$date),min(ys$date), units='days') <300) & loc>=5 & spn=="1"){ graphl<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1, 
             mapping = aes(x=date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "3 weeks", date_labels = "%d %b %y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18))+
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_wrap( ~ location_name, ncol=2) +
  theme(strip.text.x = element_text(size=16))
graphl}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>50) & (difftime(max(ys$date),min(ys$date), units='days') <300) & loc>=5 & spn=="1") {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location.  '}`

```{r fig.width=9, fig.height=8}
## date ~ percentile graph if 1 location, 1 species
#if data spans more than a year

if((difftime(max(ys$date),min(ys$date), units='days')>=300) & loc=="1" & spn=="1") {graphm<-ggplot(ys, aes(x= date, y= percentile)) +
  geom_point(ys, size=3, 
             mapping = aes(x=date, y= percentile, color=activity_level, shape=1))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "12 weeks", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(linetype="blank"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  graphm}

##end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>=300) & loc=="1" & spn=="1") {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey.  '}`

```{r fig.width=9, fig.height=8}
## date ~ percentile graph if 1 location, >1 species
#if data spans more than a year

if((difftime(max(ys$date),min(ys$date), units='days')>=300) & loc=="1" & spn>1) {graphm<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, 
             mapping = aes(x=date, y= percentile, color=activity_level, shape=1))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_discrete(labels=abbreviate)+
  scale_x_date(name = "Date", date_breaks = "12 weeks", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(species ~ .) +
  theme(strip.text.y = element_text(size=16, face="italic"))
graphm}

##end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>=300) & loc=="1" & spn>1) {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by species.  '}`


```{r fig.width=9, fig.height=10}
## date ~ percentile graph if 2-5 locations + >1 species
#if data spans more than a year

if((difftime(max(ys$date),min(ys$date), units='days')>=300) & loc>1 & loc<5 & spn>1) {graphn<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1,
             mapping = aes(x=date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "12 weeks", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(species ~ location_name) +
  theme(strip.text.y = element_text(size=16, face="italic"),
        strip.text.x = element_text(size=16))
graphn}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>=300) & loc>1 & loc<5 & spn>1) {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location and species.  '}`


```{r fig.width=9, fig.height=10}
# date ~ percentile graph if 1 species and 2-5 locations
#if data spans more than a year

if((difftime(max(ys$date),min(ys$date), units='days')>=300) & loc>1 & loc<5 & spn=="1") {graphn<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1, 
             mapping = aes(x=date, y= percentile, color=activity_level))+
  xlab(expression("Night"))+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "12 weeks", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18))+
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(. ~ location_name) +
  theme(strip.text.x = element_text(size=16))
graphn}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>=300) & loc>1 & loc<5 & spn=="1") {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location.  '}`


```{r fig.width=9, fig.height=10}
## date ~ percentile graph if >5 location + >1 species
#if data spans more than a year

if((difftime(max(ys$date),min(ys$date), units='days')>=300) & loc>=5 & spn>1) {grapho<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1,
             mapping = aes(x=date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "12 weeks", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_wrap(species ~ location_name, ncol=2) +
  theme(strip.text.y = element_text(size=16, face="italic"),
        strip.text.x = element_text(size=16))
grapho}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>=300) & loc>=5 & spn=="1") {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location and species.  '}`


```{r fig.width=9, fig.height=8}

# date ~ percentile graph if 1 species and >5 location
#if data spans more than a year
ys$date<-as.Date(ys$date, format = "%d/%m/%Y")

if((difftime(max(ys$date),min(ys$date), units='days')>=300) & loc>=5 & spn=="1"){ grapho<-ggplot(ys, aes(x= date, y= percentile))+
  geom_point(ys, size=3, shape=1, 
             mapping = aes(x=date, y= percentile, color=activity_level))+
  xlab("Night")+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_date(name = "Date", date_breaks = "12 weeks", date_labels = "%d %b %Y")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(angle=90,size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18))+
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_wrap( ~ Location, ncol=2) +
  theme(strip.text.x = element_text(size=16))
grapho}

#end code for date graph
```

`r if((difftime(max(ys$date),min(ys$date), units='days')>=300) & loc>5 & spn=="1") {'**Figure 2.**\n The activity level (percentile) of bats recorded across each night of the bat survey, split by location.  '}`

```{r}
#Code to work out median
#This is not actually used at the moment but just leaving here in case needed in future

med<-median(df$percentile)
x       = df$percentile
bootmed = apply(matrix(sample(x, rep=TRUE, 10^4*length(x)), nrow=10^4), 1, median)
medci<- quantile(bootmed, c(.025, 0.975))

medtemp<-median(df$temperature_c)

##need to make a basic dataframe with median temperature, median percentile and
#confidence intervals
titles<-c("Percentile", "Temperature","a","b")
combined<- c(med,medtemp,medci)
dfa<-data.frame(titles, combined, stringsAsFactors = FALSE)
dfb<-data.frame(titles, combined)
library(tidyr)
data_wide <- spread(dfb, titles, combined)

#end median code
```

```{r}
tempsum <- sum(ys$temperature_c) #adds up all temperature values - can use this to determine if temperature data was entered
windsum <- sum(ys$wind_speed_mph) #adds up all windspeed values - can use this to determine if windspeed data was entered
```


```{r fig.width=9, fig.height=8}
#code for the temperature graph with one location and more than one species

if(tempsum>0 & loc=="1" & spn>1) {
graphA<-ggplot(ys, aes(x=temperature_c, y= percentile))+
  geom_point(ys, size=3, shape=1,
             mapping = aes(x=temperature_c, y= percentile, color=activity_level))+
  xlab(expression("Temperature "(degree*C)))+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low")) +
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_continuous(limit=c(6,18),breaks=seq(6,18,2))+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=16),
        axis.text.x  = element_text(size=16),
        axis.text.y  = element_text(size=16),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18))+
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(species ~ .) +
  theme(strip.text.y = element_text(size=16, face="italic")) #species names in italics)
graphA}

#end code for temperature graph
```

`r if(tempsum>0 & loc=="1" & spn>1) {'**Figure 3.**\n The relationship between recorded bat activity (percentile) and the temperature at sunset, split by species.  '}`

```{r fig.width=9, fig.height=8}
#code for the temperature graph with location and one species

if(tempsum>0 & loc=="1" & spn=="1") {
graphA<-ggplot(ys, aes(x=temperature_c, y= percentile))+
  geom_point(ys, size=3, shape=1,
             mapping = aes(x=temperature_c, y= percentile, color=activity_level))+
  xlab(expression("Temperature "(degree*C)))+ #set x-axis
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low")) +
  scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
  scale_x_continuous(limit=c(6,18),breaks=seq(6,18,2))+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(linetype="blank"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=16),
        axis.text.x  = element_text(size=16),
        axis.text.y  = element_text(size=16),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18))+
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
graphA}

#end code for temperature graph
```

`r if(tempsum>0 & loc=="1" & spn=="1") {'**Figure 3.**\n The relationship between recorded activity (percentile) of bats and the temperature at sunset.  '}`

```{r fig.width=9, fig.height=10}
#code for the temperature graph with more than one location and one species

if(tempsum>0 & loc>1 & loc<5 & spn=="1") {
  graphB<-ggplot(ys, aes(x=temperature_c, y= percentile))+
    geom_point(ys, size=3, shape=1,
               mapping = aes(x=temperature_c, y= percentile, color=activity_level))+
    xlab(expression("Temperature "(degree*C)))+ #set x-axis
    ylab("Bat Activity Level (Percentile)")+
    scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                        breaks=c("High","Moderate/High","Moderate",
                                 "Low/Moderate","Low")) +
    scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
    scale_x_continuous(limit=c(6,18),breaks=seq(6,18,2))+
    theme_bw() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(colour="black", linetype="solid"),
          axis.line=element_line(size=0.5, colour="black", linetype="solid"),
          axis.title.x=element_text(size=16),
          axis.text.x  = element_text(size=16),
          axis.text.y  = element_text(size=16),
          axis.line.x = element_line(color="black", size = 0.5),
          axis.line.y = element_line(color="black", size = 0.5),
          axis.title.y=element_text(size=18))+
    geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
    geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
    geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
    geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
    facet_grid(. ~ location_name) +
    theme(strip.text.x = element_text(size=16)) #make the location labels bigger
  graphB}

#end code for temperature graph
```

`r if(tempsum>0 & loc>1 & loc<5 & spn=="1") {'**Figure 3.**\n The relationship between recorded activity (percentile) of bats and the temperature at sunset, split by location.  '}`

```{r fig.width=9, fig.height=10}
#code for the temperature graph
#if more than one location and more than one species

if(tempsum>0 & loc>1 & loc<5 & spn<1) {
  graphB<-ggplot(ys, aes(x=temperature_c, y= percentile))+
    geom_point(ys, size=3, shape=1,
               mapping = aes(x=temperature_c, y= percentile, color=activity_level))+
    xlab(expression("Temperature "(degree*C)))+ #set x-axis
    ylab("Bat Activity Level (Percentile)")+
    scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                        breaks=c("High","Moderate/High","Moderate",
                                 "Low/Moderate","Low")) +
    scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
    scale_x_continuous(limit=c(6,18),breaks=seq(6,18,2))+
    theme_bw() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(colour="black", linetype="solid"),
          axis.line=element_line(size=0.5, colour="black", linetype="solid"),
          axis.title.x=element_text(size=16),
          axis.text.x  = element_text(size=16),
          axis.text.y  = element_text(size=16),
          axis.line.x = element_line(color="black", size = 0.5),
          axis.line.y = element_line(color="black", size = 0.5),
          axis.title.y=element_text(size=18))+
    geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
    geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
    geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
    geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
    facet_grid(species ~ location_name) +
    theme(strip.text.y = element_text(size=16, face="italic"), #species names in italics
          strip.text.x = element_text(size=16)) #make the location labels bigger
  graphB}

#end code for temperature graph
```

`r if(tempsum>0 & loc>1 & loc<5 & spn<1) {'**Figure 3.**\n The relationship between recorded bat activity (percentile) and the temperature at sunset, split by species and location.  '}`

```{r fig.width=9, fig.height=10}
#code for the temperature graph
#if more than 5 locations and one species

if(tempsum>0 & loc>=5 & spn=="1") {
  graphC<-ggplot(ys, aes(x=temperature_c, y= percentile))+
    geom_point(ys, size=3, shape=1,
               mapping = aes(x=temperature_c, y= percentile, color=activity_level))+
    xlab(expression("Temperature "(degree*C)))+ #set x-axis
    ylab("Bat Activity Level (Percentile)")+
    scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                        breaks=c("High","Moderate/High","Moderate",
                                 "Low/Moderate","Low")) +
    scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
    scale_x_continuous(limit=c(6,18),breaks=seq(6,18,2))+
    theme_bw() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(colour="black", linetype="solid"),
          axis.line=element_line(size=0.5, colour="black", linetype="solid"),
          axis.title.x=element_text(size=16),
          axis.text.x  = element_text(size=16),
          axis.text.y  = element_text(size=16),
          axis.line.x = element_line(color="black", size = 0.5),
          axis.line.y = element_line(color="black", size = 0.5),
          axis.title.y=element_text(size=18))+
    geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
    geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
    geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
    geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
    facet_wrap( ~ location_name, ncol=2) +
    theme(strip.text.x = element_text(size=16)) #make the location labels bigger
  graphC}

#end code for temperature graph
```

`r if(tempsum>0 & loc>=5 & spn=="1") {'**Figure 3.**\n The relationship between recorded activity (percentile) of bats and the temperature at sunset, split by location.  '}`

```{r fig.width=9, fig.height=10}
#code for the temperature graph
#more than 5 locations and more than one species

if(tempsum>0 & loc>=5 & spn>1) {
  graphC<-ggplot(ys, aes(x=temperature_c, y= percentile))+
    geom_point(ys, size=3, shape=1,
               mapping = aes(x=temperature_c, y= percentile, color=activity_level))+
    xlab(expression("Temperature "(degree*C)))+ #set x-axis
    ylab("Bat Activity Level (Percentile)")+
    scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                        breaks=c("High","Moderate/High","Moderate",
                                 "Low/Moderate","Low")) +
    scale_y_continuous(breaks=seq(0,100,20), limits=c(0,100)) + 
    scale_x_continuous(limit=c(6,18),breaks=seq(6,18,2))+
    theme_bw() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(colour="black", linetype="solid"),
          axis.line=element_line(size=0.5, colour="black", linetype="solid"),
          axis.title.x=element_text(size=16),
          axis.text.x  = element_text(size=16),
          axis.text.y  = element_text(size=16),
          axis.line.x = element_line(color="black", size = 0.5),
          axis.line.y = element_line(color="black", size = 0.5),
          axis.title.y=element_text(size=18))+
    geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
    geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
    geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
    geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
    facet_wrap(species ~ location_name, ncol=2) +
    theme(strip.text.y = element_text(size=16, face="italic"), #species names in italics
          strip.text.x = element_text(size=16)) #make the location labels bigger
  graphC}

#end code for temperature graph
```

`r if(tempsum>0 & loc>=5 & spn>1) {'**Figure 3.**\n The relationship between recorded bat activity (percentile) and the temperature at sunset, split by species and location.  '}`

```{r fig.width=9, fig.height=10}
#windspeed graph
#if one location and more than one species
if(windsum>0 & loc=="1" & spn>1) {
graphwc<-ggplot(ys, aes(x=wind_speed_mph , y=percentile))+
  geom_point(ys, size=3, shape=1,
             mapping = aes(x=wind_speed_mph, y= percentile, color=activity_level))+
  xlab("Windspeed at Sunset (mph)")+
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20),limits=c(0,100)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black", linetype="solid"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
  facet_grid(. ~ species) +
  theme(strip.text.x = element_text(size=16, face="italic"))
graphwc}
```

`r if(tempsum>0 & windsum>0 & loc=="1" & spn>1) {'**Figure 4.**\n The relationship between recorded bat activity (percentile) and the temperature at sunset, split by species.  '} else if(tempsum=="0" & windsum>0 & loc=="1" & spn>1) {'**Figure 3.**\n The relationship between recorded bat activity (percentile) and the temperature at sunset, split by species.  '}`

```{r fig.width=9, fig.height=10}
#windspeed graph
#if one location and one species
if(windsum>0 & loc=="1" & spn=="1") {
graphwc<-ggplot(ys, aes(x=wind_speed_mph , y=percentile))+
  geom_point(ys, size=3, shape=1,
             mapping = aes(x=wind_speed_mph, y= percentile, color=activity_level))+
  xlab("Windspeed at Sunset (mph)")+
  ylab("Bat Activity Level (Percentile)")+
  scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                      breaks=c("High","Moderate/High","Moderate",
                               "Low/Moderate","Low"))+
  scale_y_continuous(breaks=seq(0,100,20),limits=c(0,100)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(linetype="blank"),
        axis.line=element_line(size=0.5, colour="black", linetype="solid"),
        axis.title.x=element_text(size=18),
        axis.text.x  = element_text(size=16),
        axis.text.y  = element_text(size=12),
        axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5),
        axis.title.y=element_text(size=18)) +
  geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
  geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
  geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
  geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
graphwc}
```

`r if(tempsum>0 & windsum>0 & loc=="1" & spn=="1") {'**Figure 4.**\n The relationship between recorded activity (percentile) of bats and the temperature at sunset.  '} else if(tempsum=="0" & windsum>0 & loc=="1" & spn=="1") {'**Figure 3.**\n The relationship between recorded activity (percentile) bats and the temperature at sunset.  '}`

```{r fig.width=9, fig.height=10}
#windspeed graph
#if between 2 and 5 locations and only one species
if(windsum>0 & loc>1 & loc<5 & spn=="1") {
  graphwd<-ggplot(ys, aes(x=wind_speed_mph, y=percentile))+
    geom_point(ys, size=3, shape=1,
               mapping = aes(x=wind_speed_mph, y=percentile, color=activity_level))+
    xlab("Windspeed at Sunset (mph)")+
    ylab("Bat Activity Level (Percentile)")+
    scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                        breaks=c("High","Moderate/High","Moderate",
                                 "Low/Moderate","Low"))+
    scale_y_continuous(breaks=seq(0,100,20),limits=c(0,100)) +
    theme_bw() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(colour="black", linetype="solid"),
          axis.line=element_line(size=0.5, colour="black", linetype="solid"),
          axis.title.x=element_text(size=18),
          axis.text.x  = element_text(size=16),
          axis.text.y  = element_text(size=12),
          axis.line.x = element_line(color="black", size = 0.5),
          axis.line.y = element_line(color="black", size = 0.5),
          axis.title.y=element_text(size=18)) +
    geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
    geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
    geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
    geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
    facet_grid(location_name ~ .) +
    theme(strip.text.x = element_text(size=16, face="italic"))
  graphwd}
```

`r if(tempsum>0 & windsum>0 & loc>1 & loc<5 & spn=="1") {'**Figure 4.**\n The relationship between recorded activity (percentile) of bats and the temperature at sunset, split by location.  '} else if(tempsum=="0" & windsum>0 & loc>1 & loc<5 & spn=="1") {'**Figure 3.**\n The relationship between recorded activity (percentile) of bats and the temperature at sunset, split by location.  '}`

```{r fig.width=9, fig.height=8}
#windspeed graph
#if between 2 and 5 locations and more than one species
if(windsum>0 & loc>1 & loc<5 & spn<1) {
  graphwd<-ggplot(ys, aes(x=wind_speed_mph , y=percentile))+
    geom_point(ys, size=3, shape=1,
               mapping = aes(x=wind_speed_mph, y= percentile, color=activity_level))+
    xlab("Windspeed at Sunset (mph)")+
    ylab("Bat Activity Level (Percentile)")+
    scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                        breaks=c("High","Moderate/High","Moderate",
                                 "Low/Moderate","Low"))+
    scale_y_continuous(breaks=seq(0,100,20),limits=c(0,100)) +
    theme_bw() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(colour="black", linetype="solid"),
          axis.line=element_line(size=0.5, colour="black", linetype="solid"),
          axis.title.x=element_text(size=18),
          axis.text.x  = element_text(size=16),
          axis.text.y  = element_text(size=12),
          axis.line.x = element_line(color="black", size = 0.5),
          axis.line.y = element_line(color="black", size = 0.5),
          axis.title.y=element_text(size=18)) +
    geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
    geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
    geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
    geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
    facet_grid(species ~ location_name) +
    theme(strip.text.y = element_text(size=16, face="italic"), #species names in italics
          strip.text.x = element_text(size=16)) #make the location labels bigger
  graphwd}
```

`r if(tempsum>0 & windsum>0 & loc>1 & loc<5 & spn<1) {'**Figure 4.**\n The relationship between recorded bat activity (percentile) and the temperature at sunset, split by location and species.  '} else if(tempsum=="0" & windsum>0 & loc>1 & loc<5 & spn<1) {'**Figure 3.**\n The relationship between recorded bat activity (percentile) and the temperature at sunset, split by location and species.  '}`

```{r fig.width=9, fig.height=8}
#windspeed graph
#if more than 5 locations but only one species
if(windsum>0 & loc>=5 & spn=="1") {
  graphwe<-ggplot(ys, aes(x=wind_speed_mph , y=percentile))+
    geom_point(ys, size=3, shape=1,
               mapping = aes(x=wind_speed_mph, y= percentile, color=activity_level))+
    xlab("Windspeed at Sunset (mph)")+
    ylab("Bat Activity Level (Percentile)")+
    scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                        breaks=c("High","Moderate/High","Moderate",
                                 "Low/Moderate","Low"))+
    scale_y_continuous(breaks=seq(0,100,20),limits=c(0,100)) +
    theme_bw() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(colour="black", linetype="solid"),
          axis.line=element_line(size=0.5, colour="black", linetype="solid"),
          axis.title.x=element_text(size=18),
          axis.text.x  = element_text(size=16),
          axis.text.y  = element_text(size=12),
          axis.line.x = element_line(color="black", size = 0.5),
          axis.line.y = element_line(color="black", size = 0.5),
          axis.title.y=element_text(size=18)) +
    geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
    geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
    geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
    geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
    facet_wrap( ~ location_name, ncol=2) +
    theme(strip.text.x = element_text(size=16, face="italic"))
  graphwe}
```

`r if(tempsum>0 & windsum>0 & loc>=5 & spn=="1") {'**Figure 4.**\n The relationship between recorded activity (percentile) of bats and the temperature at sunset, split by location.  '} else if(tempsum=="0" & windsum>0 & loc>5 & spn=="1") {'**Figure 3.**\n The relationship between recorded activity (percentile) of bats and the temperature at sunset, split by location.  '}`

```{r fig.width=9, fig.height=8}
#windspeed graph
#if more than 5 locations and more than one species
if(windsum>0 & loc>=5 & spn>1) {
  graphwe<-ggplot(ys, aes(x = wind_speed_mph, y = percentile))+
    geom_point(ys, size=3, shape=1,
               mapping = aes(x = wind_speed_mph, y = percentile, color = activity_level))+
    xlab("Windspeed at Sunset (mph)")+
    ylab("Bat Activity Level (Percentile)")+
    scale_colour_manual(values=cbbPalette, name="Activity\nLevel",
                        breaks=c("High","Moderate/High","Moderate",
                                 "Low/Moderate","Low"))+
    scale_y_continuous(breaks=seq(0,100,20),limits=c(0,100)) +
    theme_bw() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(colour="black", linetype="solid"),
          axis.line=element_line(size=0.5, colour="black", linetype="solid"),
          axis.title.x=element_text(size=18),
          axis.text.x  = element_text(size=16),
          axis.text.y  = element_text(size=12),
          axis.line.x = element_line(color="black", size = 0.5),
          axis.line.y = element_line(color="black", size = 0.5),
          axis.title.y=element_text(size=18)) +
    geom_hline(aes(yintercept=20), linetype="dashed", color="#0072B2") +
    geom_hline(aes(yintercept=40), linetype="dashed", color="#56B4E9") +
    geom_hline(aes(yintercept=60), linetype="dashed", color="#009E73") +
    geom_hline(aes(yintercept=80), linetype="dashed", color="#E69F00") +
    facet_wrap(species ~ location_name, ncol=2) +
    theme(strip.text.y = element_text(size=16, face="italic"), #species names in italics
          strip.text.x = element_text(size=16)) #make the location labels bigger
  graphwe}
```

`r if(tempsum>0 & windsum>0 & loc>=5 & spn>1) {'**Figure 4.**\n The relationship between recorded bat activity (percentile) and the temperature at sunset, split by location and species.  '} else if(tempsum=="0" & windsum>0 & loc>5 & spn>1) {'**Figure 3.**\n The relationship between recorded bat activity (percentile) and the temperature at sunset, split by location and species.  '}`